Visual Diagnostics for Constrained Optimisation with Application to Guided Tours

### 2021-01-27 paper/zhang-cook-laa-langrene-menendez.tex
update code for scale color as per the latest ferrn

\caption[A selected number of frames from the animated PCA plot]{A selected number of frames from the animated PCA plot. With animation, it is easier to track the progression from the start to finish in each algorithm.}\label{fig:toy-pca-animated}
\end{figure}
\end{Schunk}

>>>>

\caption{A selected number of frames from the animated PCA plots. With animation, it is easier to track the progression of each optimiser from the start to finish. A full video of this aimation can be found at \url{https://vimeo.com/user132007430/review/504242845/b73f37175a}}\label{fig:toy-pca-animated}
\end{figure}
\end{Schunk}
